Can historical data predict population responses to climate change experiments?

### 2017-08-04 precip/manuscript/overall_prediction_score.tex
adding a bunch of old edits to scripts and manuscript files

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Thu Dec 22 04:09:23 2016
\begin{table}[ht]
\centering
\caption{Comparison of model predictions from climate model and year effects model for each species and vital rate.  Two prediction scores are reported, MSE and lppd. Lower MSE indicates improved predictions whereas higher lppd indicates improved predictions.  Instances where the climate model outperformed the random year effects model are marked with "***" in the last column. ARTR = \textit{A. tripartita}, HECO = \textit{H. comata}, POSE = \textit{P. secunda}, PSSP = \textit{P. spicata}.} 
\label{table:overallPreds}
\begin{tabular}{lllrrrl}
  \hline
species & vital\_rate & score & climate model & year effects model & diff & improved \\ 
  \hline
ARTR & growth & lppd & -186.08 & -189.17 & 3.09 & *** \\ 
  ARTR & growth & MSE & 0.55 & 0.55 & -0.00 & *** \\ 
  ARTR & recruitment & lppd & -79.05 & -77.81 & -1.24 &  \\ 
  ARTR & recruitment & MSE & 169.86 & 9.47 & 160.39 &  \\ 
  ARTR & survival & lppd & -37.55 & -36.42 & -1.13 &  \\ 
  ARTR & survival & MSE & 0.06 & 0.06 & 0.00 &  \\ 
  HECO & growth & lppd & -475.54 & -454.36 & -21.18 &  \\ 
  HECO & growth & MSE & 1.26 & 1.18 & 0.09 &  \\ 
  HECO & recruitment & lppd & -149.43 & -151.60 & 2.17 & *** \\ 
  HECO & recruitment & MSE & 288.16 & 235.57 & 52.59 &  \\ 
  HECO & survival & lppd & -158.99 & -147.06 & -11.93 &  \\ 
  HECO & survival & MSE & 0.12 & 0.11 & 0.01 &  \\ 
  POSE & growth & lppd & -1823.71 & -1831.56 & 7.85 & *** \\ 
  POSE & growth & MSE & 1.72 & 1.73 & -0.01 & *** \\ 
  POSE & recruitment & lppd & -260.05 & -257.46 & -2.59 &  \\ 
  POSE & recruitment & MSE & 45.40 & 37.32 & 8.08 &  \\ 
  POSE & survival & lppd & -698.06 & -718.60 & 20.54 & *** \\ 
  POSE & survival & MSE & 0.14 & 0.14 & -0.00 & *** \\ 
  PSSP & growth & lppd & -1232.93 & -1237.92 & 4.99 & *** \\ 
  PSSP & growth & MSE & 1.51 & 1.51 & 0.00 &  \\ 
  PSSP & recruitment & lppd & -271.34 & -273.94 & 2.60 & *** \\ 
  PSSP & recruitment & MSE & 79.09 & 42.68 & 36.41 &  \\ 
  PSSP & survival & lppd & -332.47 & -307.26 & -25.21 &  \\ 
  PSSP & survival & MSE & 0.11 & 0.10 & 0.01 &  \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Fri Dec 23 14:08:37 2016
\begin{table}[ht]
\centering
\caption{Comparison of model predictions from climate model and no climate model for each species and vital rate.  Two prediction scores are reported, MSE and lppd. Lower MSE indicates improved predictions whereas higher lppd indicates improved predictions.  Instances where the climate model outperformed the no climate model are marked with "***" in the last column. ARTR = \textit{A. tripartita}, HECO = \textit{H. comata}, POSE = \textit{P. secunda}, PSSP = \textit{P. spicata}.} 
\label{table:overallPreds}
\begin{tabular}{lllrrrl}
  \hline
species & vital\_rate & score & climate model & baseline model & diff & improved \\ 
  \hline
ARTR & growth & lppd & -186.08 & -189.17 & 3.09 & *** \\ 
  ARTR & growth & MSE & 0.55 & 0.55 & -0.00 & *** \\ 
  ARTR & recruitment & lppd & -79.05 & -77.81 & -1.24 &  \\ 
  ARTR & recruitment & MSE & 169.86 & 9.47 & 160.39 &  \\ 
  ARTR & survival & lppd & -37.55 & -36.42 & -1.13 &  \\ 
  ARTR & survival & MSE & 0.06 & 0.06 & 0.00 &  \\ 
  HECO & growth & lppd & -475.54 & -454.36 & -21.18 &  \\ 
  HECO & growth & MSE & 1.26 & 1.18 & 0.09 &  \\ 
  HECO & recruitment & lppd & -149.43 & -151.60 & 2.17 & *** \\ 
  HECO & recruitment & MSE & 288.16 & 235.57 & 52.59 &  \\ 
  HECO & survival & lppd & -158.99 & -147.06 & -11.93 &  \\ 
  HECO & survival & MSE & 0.12 & 0.11 & 0.01 &  \\ 
  POSE & growth & lppd & -1823.71 & -1831.56 & 7.85 & *** \\ 
  POSE & growth & MSE & 1.72 & 1.73 & -0.01 & *** \\ 
  POSE & recruitment & lppd & -260.05 & -257.46 & -2.59 &  \\ 
  POSE & recruitment & MSE & 45.40 & 37.32 & 8.08 &  \\ 
  POSE & survival & lppd & -698.06 & -718.60 & 20.54 & *** \\ 
  POSE & survival & MSE & 0.14 & 0.14 & -0.00 & *** \\ 
  PSSP & growth & lppd & -1232.93 & -1237.92 & 4.99 & *** \\ 
  PSSP & growth & MSE & 1.51 & 1.51 & 0.00 &  \\ 
  PSSP & recruitment & lppd & -271.34 & -273.94 & 2.60 & *** \\ 
  PSSP & recruitment & MSE & 79.09 & 42.68 & 36.41 &  \\ 
  PSSP & survival & lppd & -332.47 & -307.26 & -25.21 &  \\ 
  PSSP & survival & MSE & 0.11 & 0.10 & 0.01 &  \\ 
   \hline
\end{tabular}
\end{table}

### 2017-08-04 precip/manuscript/pgr_predictions.tex
adding a bunch of old edits to scripts and manuscript files

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Thu Dec 22 04:07:36 2016
\begin{table}[!h]
\centering
\caption{MSE of predicted log cover changes and correlations between log cover changes predicted and observed. Predictions for the cover changes in the experimental plots were generated either from the year effects or the climate models. Instances where the climate model made better predictions than the year effects model are indicated with the "***". ARTR = \textit{A. tripartita}, HECO = \textit{H. comata}, POSE = \textit{P. secunda}, PSSP = \textit{P. spicata}.} 
\label{table:corPGR}
\begin{tabular}{rllrrrl}
  \hline
 & species & stat & year effects model & climate model & diff & improved \\ 
  \hline
1 & ARTR & cor & 0.48 & 0.19 & -0.29 &  \\ 
  2 & ARTR & MSE & 0.30 & 0.30 & 0.00 &  \\ 
  3 & HECO & cor & 0.29 & 0.22 & -0.07 &  \\ 
  4 & HECO & MSE & 0.49 & 0.57 & 0.07 &  \\ 
  5 & POSE & cor & 0.45 & 0.53 & 0.07 & *** \\ 
  6 & POSE & MSE & 0.42 & 0.41 & -0.01 & *** \\ 
  7 & PSSP & cor & 0.36 & 0.38 & 0.03 & *** \\ 
  8 & PSSP & MSE & 0.39 & 0.39 & -0.01 & *** \\ 
   \hline
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.3.1 by xtable 1.8-2 package
% Tue Jan 17 13:20:20 2017
\begin{table}[H]
\centering
\caption{MSE of predicted log cover changes and correlations between log cover changes predicted and observed. Predictions for the cover changes in the experimental plots were generated either from the climate or no climate models. Instances where the climate model made better predictions than the no climate model are indicated with the "***". ARTR = \textit{A. tripartita}, HECO = \textit{H. comata}, POSE = \textit{P. secunda}, PSSP = \textit{P. spicata}.} 
\label{table:corPGR}
\begin{tabular}{rllrrrl}
  \hline
 & species & stat & baseline model & climate model & diff & improved \\ 
  \hline
1 & ARTR & cor & 0.48 & 0.19 & -0.29 &  \\ 
  2 & ARTR & MSE & 0.30 & 0.30 & 0.00 &  \\ 
  3 & HECO & cor & 0.29 & 0.22 & -0.07 &  \\ 
  4 & HECO & MSE & 0.49 & 0.57 & 0.07 &  \\ 
  5 & POSE & cor & 0.45 & 0.53 & 0.07 & *** \\ 
  6 & POSE & MSE & 0.42 & 0.41 & -0.01 & *** \\ 
  7 & PSSP & cor & 0.36 & 0.38 & 0.03 & *** \\ 
  8 & PSSP & MSE & 0.39 & 0.39 & -0.01 & *** \\ 
   \hline
\end{tabular}
\end{table}
